\section{Introduction}
Blood flow imaging of the brain has brought insights to neuroscience for over 50 years.\cite{Taber_2005} Computation of whole-brain, or global, cerebral blood flow (gCBF) from blood flow images is important both when gCBF is an outcome measure of interest in its own right and when gCBF fluctuations create a nuisance that complicates identifying or interpreting relative changes in regional blood flow (rCBF).\cite{Small_2004} 

Early approaches for computing gCBF from positron emission tomography (PET) images included averaging over voxels remaining after a fixed threshold was applied as a percentage of peak rCBF; this was needed because of incomplete axial coverage of the brain from early scanners, and was reproducible because the images had low spatial resolution.\cite{6609680} Another early approach used regional sampling of CBF images to estimate gCBF.\cite{6971299}\cite{Perlmutter_1985} Eventually, technical advances in PET image resolution, structural imaging, computational power and cross-modal image registration allowed gCBF to be directly averaged across every voxel in the brain.

PET CBF images are made most commonly using the ``autoradiographic'' technique, i.e. by summing radioactivity over an interval of time after administration of the radiotracer. These images are created by greater or lesser amounts of radiation flowing to different parts of the head, so voxels with higher positive numbers reflect greater CBF, and all voxel values are nonnegative (to the accuracy limits of the reconstruction algorithm). When the arterial input function is measured, these images can be converted to a quantitative CBF map by scaling voxels multiplicatively based on their intensity.[ref. here from an early ``pie chart'' type paper] In fact, to a reasonable approximation, the scaling factor is constant across the image.[find a ref to go here from an early paper that used nonquantitative PET CBF images in SPM] In many settings, changes in gCBF can be ignored by scaling all images to similar values. For our purposes, the key implication of the foregoing information is that multiplicative scaling is an appropriate approach to equalizing the intensity of two autoradiographic CBF images.

By contrast, perfusion images from arterial spin labeling (ASL) MRI are created by subtracting two images obtained a few seconds apart, one in which arterial blood flowing into the brain has been labeled using a spatially limited radio frequency pulse (``tag'') and a second image without that label (``control'').[Add a citation here to an early ref here for cASL and one for pASL, or cite a review of ASL methods.] Subtraction creates the possibility of a negative or positive additive bias across a CBF image, in which case additive rather than multiplicative correction may better equalize the intensity of two ASL CBF images.

Here we test that hypothesis using a set of ASL images acquired in \sout{2006-2008?} as part of a pharmacological challenge MRI study in Parkinson disease (PD).\cite{Black_2010} Newer ASL implementations likely produce images of higher quality, but for the purpose of comparing correction methods, these older images may provide a more stringent test.