\section{Results}
We assessed the effect of additive or multiplicative intensity equalization in several ways: by examining the voxel intensity distribution (by frequency histogram), by judging image quality visually and by quantitative GM:WM CBF ratios, and by the suitability of each set of images for detecting appropriate brain activation with visual stimulation.

\subsection{Voxel intensity distribution (histogram)}
The mean $\pm$ SD ratio for the original CBF images was $MMM \pm SSS$. The original CBF images contained a reasonable distribution of voxel intensities except that they appeared shifted leftwards to varying degrees, so that many voxels in the brain had physiologically impossible negative values (the 3 curves in the histogram in the first row of Fig. \ref{fig:rgb_figure} reflect three successive ASL images from the same subject; a transverse section from each of these images is shown to the right of the histogram). Multiplicative normalization of course produced an image with an equal fraction of negative voxel values, though the normalized image's mode was now 50 (histograms in second row of Fig. \ref{fig:rgb_figure}). Additive normalization produced a voxel intensity distribution that reflects the physiological expectation and much more accurately matches the intensity distributions across the normalized images (histograms in third row of Fig. \ref{fig:rgb_figure}). 

\subsection{Image quality}
Images normalized additively (third row in Fig. \ref{fig:rgb_figure}) present much clearer and much more uniform gray:white contrast on visual inspection. We tested this impression quantitatively using the GM and WM CBF, and their ratio, across scans within subjects and across subjects. (Here we put the values for GM, WM, and GM:WM ratio, both within subject and across subjects.)

\begin{table}
\begin{tabular}{lcccc}
  \textbf{Image set} & \textbf{SD GM within subject} & \textbf{SD WM within subject} & \textbf{blah blah} & \textbf{blah blah} \\
  non-normalized & x.xxx & y.yy & z.zzz & w.ww \\
  additively normalized & x.xxx & y.yy & z.zzz & w.ww \\
  multiplicatively normalized & x.xxx & y.yy & z.zzz & w.ww \\
\end{tabular}
\caption{\textbf{Task activation with visual stimulation}}
\label{table:taskVOI}
\end{table}

\subsection{Task activation: \textit{a priori} volume of interest}
We examined the effect of visual stimulation in the partial visual cortex VOI (intended as a positive control) and in the whole-brain WM VOI (intended as a negative control). As shown in Table \ref{table:taskVOI}), the statistical significance of the increased rCBF in visual cortex is slightly higher in the additively normalized images, \sout{and blah blah in WM}

\begin{table}
\begin{tabular}{lcccc}
  \textbf{Image set} & \textbf{visual mean change} & \textbf{visual t (XX df)} &        \textbf{WM mean change} & \textbf{WM t (XX df)} \\
  non-normalized & x.xxx & y.yy & z.zzz & w.ww \\
  additively normalized & x.xxx & y.yy & z.zzz & w.ww \\
  multiplicatively normalized & x.xxx & y.yy & z.zzz & w.ww \\
\end{tabular}
\caption{\textbf{Task activation with visual stimulation}}
\label{table:taskVOI}
\end{table}
.

\subsection{Task activation: statistical image} With this substantial visual stimulus, SPM analyses of visual stimulation found significant clusters even without normalization, though normalization improved the signal (see Table \ref{table:SPMresults} and Supplemental Data).

\begin{table}
\begin{tabular}{lccc}
  \textbf{Image set} & \textbf{peak t (XX df)} & \textbf{cluster volume (voxels)} & \textbf{p (FDR)} \\
  non-normalized & x.xxx & yyyy & z.zzz \\
  additively normalized & x.xxx & yyyy & z.zzz \\
  multiplicatively normalized & x.xxx & yyyy & z.zzz \\
\end{tabular}
\caption{\textbf{Summary of SPM results}}
\label{table:SPMresults}
\end{table}
